A Simplified Plackett-Luce Likelihood Function for Rank Orders

### 2024-09-03 inst/hankin-AustrianJournalofStatistics.tex
replace data with actual observations from parkrun_results.txt

``Parkrun'' is a distributed community initiative that organises
weekly timed 5 km runs/walks in parks worldwide~\citep{hindley2020}.
A typical event will have 200 participants.  Table~\ref{parkruntable}
shows the author has completed a total of 15 parkruns to date,
comprising 10 runs in Auckland and 5 at Stirling.  From the first pair
of numbers we see that 238 runners attended that particular parkrun,
of whom the author placed 173.

\begin{table}[t]
  \centering
  \caption{Parkrun results}
\label{parkruntable}
\begin{tabular}{ccccccccccc}
  \\
 & \multicolumn{10}{c}{Auckland}\\
rank    & 163  & 155 & 162 & 189 & 171 & 219 & 167 & 212 & 206 & 142 \\
runners & 238  & 238 & 196 & 242 & 242 & 318 & 259 & 305 & 297 & 241 \\ \\ \\
\end{tabular}
\begin{tabular}{cccccc}
  & \multicolumn{5}{c}{Stirling}\\
rank   & 118  & 224 & 128 & 115 & 183 \\
runners& 179  & 338 & 203 & 245 & 254 \\
\end{tabular}
\end{table}

>>>>

``Parkrun'' is a distributed community initiative that organises
weekly timed 5 km runs/walks in parks worldwide~\citep{hindley2020}.
A typical event will have 200 participants.  Table~\ref{parkruntable}
shows the author has completed a total of 21 parkruns to date,
comprising 9 runs in Auckland and 12 at Stirling.  From the first pair
of numbers we see that 259 runners attended that particular parkrun at
Auckland, of whom the author placed 177.

\begin{table}[t]
  \centering
  \caption{Parkrun results}
\label{parkruntable}
\begin{tabular}{cccccccccc}\\
 & \multicolumn{9}{c}{Auckland}\\
rank   & 177& 222& 206& 142& 118& 224& 128& 115& 183\\
runners& 259& 305& 297& 241& 179& 338& 203& 245& 254\\ \\
\end{tabular}
\begin{tabular}{ccccccccccccc}
  & \multicolumn{12}{c}{Stirling}\\
rank   &  193& 240& 197& 257& 227& 234& 238& 238& 196& 242& 242& 318\\
runners&  145& 157& 156& 191& 172& 174& 173& 165& 172& 199& 181& 229\\
\end{tabular}
\end{table}
